---
title: "Plots Type I & Power"
author: "Koch, J.M.B. (Michael)"
date: '2022-05-02'
output: html_document
---

```{r, echo=F}
knitr::opts_chunk$set(echo = F, message = F)
```

# Step1: Prepearations

```{r, message = F, warning = F}
# load packages outside of simulation
library(papaja)
library(patchwork)
#source required functions & parameters
source('~/OneDrive/ms/thesis/R/functions.R')
source('~/OneDrive/ms/thesis/R/parameters.R')
```

```{r}
# load results
resultsSVNP <- read.csv("~/OneDrive/ms/thesis/output/resultsSVNP.csv", 
                        sep = " ", 
                        header = TRUE)
convSVNP <- read.csv("~/OneDrive/ms/thesis/output/convSVNP.csv",
                     sep = " ",
                     header = TRUE)
```


## Post-process

```{r}
resultsSVNP <- 
  resultsSVNP %>% 
  arrange(sigma, N, cross, iteration) %>% 
  mutate(sigmaSqu = sigma^2,
         biasCrossMean_1 = abs(crossEstMean_1 - cross),
         biasCrossMean_2 = abs(crossEstMean_2 - 0),
         biasCrossMean_3 = abs(crossEstMean_3 - 0),
         biasCrossMean_4 = abs(crossEstMean_4 - 0),
         biasCrossMean_5 = abs(crossEstMean_5 - 0),
         biasCrossMean_6 = abs(crossEstMean_6 - cross),
         condID = rep(1:(nrow(condPop)*nrow(condSVNP)), each = nIter) 
) 
  
```

# Step 2: Compute Type I error rate and Power

## Type I error rate

```{r}
# For Tresholdvariables: 1 = nonZero, 0 = zero
# For CI variables: 0 = nonZero, 1 = zero
#TypeISVNP <- 
 resultsSVNP %>% 
  select(
        isZeroTres0.10Mean_1:isZero50CI_6,
        cross,
        sigmaSqu,
        N, 
        pos,
        iteration,
        ) %>% 
  group_by(N, sigmaSqu, cross) %>% 
  summarise(typeITres0.15Mean_2 = mean(isZeroTres0.15Mean_2),
            typeITres0.15Mean_3 = mean(isZeroTres0.15Mean_3),
            typeITres0.15Mean_4 = mean(isZeroTres0.15Mean_4),
            typeITres0.15Mean_5 = mean(isZeroTres0.15Mean_5),
            typeITres0.10Mean_2 = mean(isZeroTres0.10Mean_2),
            typeITres0.10Mean_3 = mean(isZeroTres0.10Mean_3),
            typeITres0.10Mean_4 = mean(isZeroTres0.10Mean_4),
            typeITres0.10Mean_5 = mean(isZeroTres0.10Mean_5),
            typeITres0.05Mean_2 = mean(isZeroTres0.05Mean_2),
            typeITres0.05Mean_3 = mean(isZeroTres0.05Mean_3),
            typeITres0.05Mean_4 = mean(isZeroTres0.05Mean_4),
            typeITres0Mean_5 = mean(isZeroTres0Mean_5),
            typeITres0Mean_2 = mean(isZeroTres0Mean_2),
            typeITres0Mean_3 = mean(isZeroTres0Mean_3),
            typeITres0Mean_4 = mean(isZeroTres0Mean_4),
            typeITres0Mean_5 = mean(isZeroTres0Mean_5),
            typeICI95Mean_2 = mean(isZero95CI_2 == 0), 
            typeICI95Mean_3 = mean(isZero95CI_3 == 0),
            typeICI95Mean_4 = mean(isZero95CI_4 == 0),
            typeICI95Mean_5 = mean(isZero95CI_5 == 0),
            typeICI90Mean_2 = mean(isZero90CI_2 == 0), 
            typeICI90Mean_3 = mean(isZero90CI_3 == 0),
            typeICI90Mean_4 = mean(isZero90CI_4 == 0),
            typeICI90Mean_5 = mean(isZero90CI_5 == 0),
            typeICI80Mean_2 = mean(isZero80CI_2 == 0), 
            typeICI80Mean_3 = mean(isZero80CI_3 == 0),
            typeICI80Mean_4 = mean(isZero80CI_4 == 0),
            typeICI80Mean_5 = mean(isZero80CI_5 == 0),
            typeICI50Mean_2 = mean(isZero50CI_2 == 0), 
            typeICI50Mean_3 = mean(isZero50CI_3 == 0),
            typeICI50Mean_4 = mean(isZero50CI_4 == 0),
            typeICI50Mean_5 = mean(isZero50CI_5 == 0),
        N = mean(N),
        cross = mean(cross),
        sigmaSqu = mean(sigmaSqu))
```

## Power

```{r}
# For Tresholdvariables: 1 = nonZero, 0 = zero
# For CI variables: 0 = nonZero, 1 = zero
#PowerSVNP <- 
 resultsSVNP %>% 
  group_by(N, sigmaSqu, cross) %>% 
  summarise(powerTres0.15Mean_1 = mean(isZeroTres0.15Mean_1), 
            powerTres0.15Mean_6 = mean(isZeroTres0.15Mean_6), 
            powerTres0.10Mean_1 = mean(isZeroTres0.10Mean_1), 
            powerTres0.10Mean_6 = mean(isZeroTres0.10Mean_6), 
            powerTres0.05Mean_1 = mean(isZeroTres0.05Mean_1), 
            powerTres0.05Mean_6 = mean(isZeroTres0.05Mean_6),
            powerTres0Mean_1 = mean(isZeroTres0Mean_1), 
            powerTres0Mean_6 = mean(isZeroTres0Mean_6),
            powerCI95Mean_1 = mean(isZero95CI_1 == 0),
            powerCI95Mean_6 = mean(isZero95CI_6 == 0),
            powerCI90Mean_1 = mean(isZero90CI_1 == 0),
            powerCI90Mean_6 = mean(isZero90CI_6 == 0),
            powerCI80Mean_1 = mean(isZero80CI_1 == 0),
            powerCI80Mean_6 = mean(isZero80CI_6 == 0),
            powerCI50Mean_1 = mean(isZero50CI_1 == 0),
            powerCI50Mean_6 = mean(isZero50CI_6 == 0),
        N = mean(N),
        cross = mean(cross),
        sigmaSqu = mean(sigmaSqu), 
        X2.5._1 = mean(X2.5._1),
        X97.5._1 = mean(X97.5._1)) %>% 
  select(N, sigmaSqu, cross, powerCI95Mean_1, powerCI95Mean_6)
  
```


# Plots

## Ratio of correct identification

See Figure 5 p.7 Zhang et al. 

## ROC

Stappen:
- TypeI error rate &  Power (True Positive rate) middelen over de 4, ofwel 2 items. 
- Op X-as type I (false pos), op Y-as power (true-pos)
- Group/ col = sigma^2
- N = facet-wrap

=> ff kijken wat er gebeurd
=> Kan straks makkelijk uitgebreid worden op basis van andere selectiecriteria

KLAAR