---
title: "Analyzing the results" 
author: "Michael Koch"
date: "07-03-2022"
output: html_document
---

# Working through the results of the Mini- (/ Pilot-) simulation for the SVNP


# Step1: Prepearations

```{r, message = F, warning = F}
# load packages outside of simulation
library(papaja)
library(patchwork)
#source required functions & parameters
source('~/OneDrive/ms/thesis/R/functions.R')
source('~/OneDrive/ms/thesis/R/parameters.R')
```

```{r}
# load results
resultsSVNP <- read.csv("~/OneDrive/ms/thesis/output/resultsSVNP.csv", 
                        sep = " ", 
                        header = TRUE)
convSVNP <- read.csv("~/OneDrive/ms/thesis/output/convSVNP.csv",
                     sep = " ",
                     header = TRUE)
```

```{r, chache=T}
# inspect a bit
nrow(resultsSVNP)
```

```{r}
range(resultsSVNP$pos)
```

```{r}
length(resultsSVNP$pos) == length(unique(resultsSVNP$pos))
```

# Post-process

Arrange the data based on conditions and iteration, change the biases of the cross-loadings (wrongly computed for some reason), and add a sigma squared column, and a condition identifier.


```{r}
resultsSVNP <- 
  resultsSVNP %>% 
  arrange(sigma, N, cross, iteration) %>% 
  mutate(sigmaSqu = sigma^2,
         biasCrossMean_1 = abs(crossEstMean_1 - cross),
         biasCrossMean_2 = abs(crossEstMean_2 - 0),
         biasCrossMean_3 = abs(crossEstMean_3 - 0),
         biasCrossMean_4 = abs(crossEstMean_4 - 0),
         biasCrossMean_5 = abs(crossEstMean_5 - 0),
         biasCrossMean_6 = abs(crossEstMean_6 - cross),
         condID = rep(1:(nrow(condPop)*nrow(condSVNP)), each = nIter) 
) 
  
```


## Convergence

Let's explore the convergence a bit


### Divergent transitions

Not a single divergent transition

```{r}
totalSumDiv <- sum(convSVNP$sumDiv)
totalSumDiv 
```


### Effective Sample Size
```{r}
nIter
```

```{r}
convSVNP %>% 
  filter(parameter == "n_eff") %>% 
  select(lambdaMainC.1.:theta.6.)%>% 
  map_df(function(x){x/samplePars$nSampling}) %>%
  map_df(function(x){x> 0.50}) %>% 
  map_df(sum) %>% 
  map_df(function(x){ x/ 2400}) 
```

Not a single parameter with a MINIMUM effective sample size of smaller than 50% of the total sample size

### R-Hat

```{r}
convSVNP %>% 
  filter(parameter == "Rhat") %>% 
  map_df(max) %>% 
  map_df(function(x){x < 1.05}) %>% 
  select(lambdaMainC.1.:theta.6.)
```

Not a single parameter where the MAXIMUM Rhat IS NOT < 1.005


### Max Treedepth

```{r}
convSVNP %>% 
  filter(parameter == "Rhat") %>% 
  select(maxTree) %>% 
  map_df(max) 
```

FF met Sara bespreken, maar dit is meer over efficientie dan validiteit van de output, dus het zit sws wel goed!




# Plots

## Bias Mean Estimates 

### Cross-Loadings
```{r}
crossLoading1 <- 
resultsSVNP %>% 
  select(N, biasCrossMean_1, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
    cross, label) %>% 
  summarise(meanBiasCrossMean_1 = mean(biasCrossMean_1)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasCrossMean_1, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = NULL,
      y = "Mean Absolute Bias",
      title = "Cross-Loading 1")+
  ylim(0, 0.5)+
  theme_apa()

```

```{r}
crossLoading2 <- 
resultsSVNP %>% 
  select(N, biasCrossMean_2, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
    cross, label) %>% 
  summarise(meanBiasCrossMean_2 = mean(biasCrossMean_2)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasCrossMean_2, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = NULL,
       y = NULL,
      # y = "Mean Absolute Bias",
      title = "Cross-Loading 2")+
  ylim(0, 0.5)+
  theme_apa()
```


```{r}
crossLoading3 <- 
resultsSVNP %>% 
  select(N, biasCrossMean_3, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
    cross, label) %>% 
  summarise(meanBiasCrossMean_3 = mean(biasCrossMean_3)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasCrossMean_3, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = NULL,
      y = "Mean Absolute Bias",
      title = "Cross-Loading 3")+
  ylim(0, 0.5)+
  theme_apa()
```

```{r}
crossLoading4 <- 
resultsSVNP %>% 
  select(N, biasCrossMean_4, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
    cross, label) %>% 
  summarise(meanBiasCrossMean_4 = mean(biasCrossMean_4)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasCrossMean_4, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = NULL,
       y = NULL,
      title = "Cross-Loading 4")+
  ylim(0, 0.5)+
  theme_apa()
```

```{r}
crossLoading5 <- 
resultsSVNP %>% 
  select(N, biasCrossMean_5, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
    cross, label) %>% 
  summarise(meanBiasCrossMean_5 = mean(biasCrossMean_5)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasCrossMean_5, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = "Size Cross Loading",
       y = "Mean Absolute Bias",
      title = "Cross-Loading 5")+
  ylim(0, 0.5)+
  theme_apa()
```

```{r}
crossLoading6 <- 
resultsSVNP %>% 
  select(N, biasCrossMean_6, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
    cross, label) %>% 
  summarise(meanBiasCrossMean_6 = mean(biasCrossMean_6)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasCrossMean_6, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(
        x = "Size Cross Loading",
       y = NULL,
      title = "Cross-Loading 6")+
  ylim(0, 0.5)+
  theme_apa()

```
```{r, fig.height=12}
crossLoadings <- crossLoading1 + crossLoading2  + crossLoading3 + crossLoading4 + crossLoading5 + crossLoading6
crossLoadings + plot_layout(guides = "collect", ncol = 2) & theme(legend.position = "bottom", legend.title = element_blank())
```
```{r}
png(file = "~/Downloads/crossLoadings.png", width=400, height=600)
crossLoadings + plot_layout(guides = "collect", ncol = 2) & theme(legend.position = "bottom", legend.title = element_blank())
dev.off()
```


```{r}
resultsSVNP %>% 
  select(crossEstMean_1:crossEstMean_6, sigma, cross) %>% 
  group_by(sigma, cross) %>% 
    summarise_all(mean)
```

### Factor Correlation


```{r}
factCorr <- 
resultsSVNP %>% 
  select(N, biasFactCorrMean, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiasFactCorrMean = mean(biasFactCorrMean)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasFactCorrMean, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = "Size Cross Loading",
       y = "Mean Absolute Bias",
      title = "Factor Correlation")+
  ylim(0, 0.5)+
  theme_apa()
factCorr
```
```{r}
 
png(file = "~/Downloads/factCorr.png", width=300, height=250)
factCorr + plot_layout(guides = "collect", ncol = 2) & theme(legend.position = "bottom", legend.title = element_blank())
dev.off()
```


### Main Loadings

```{r}
mainLoading1 <- 
resultsSVNP %>% 
  select(N, biasMainMean_1, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiasMainMean_1 = mean(biasMainMean_1)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasMainMean_1, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = NULL,
       y = "Mean Absolute Bias",
      title = "Main Loading 1")+
  ylim(0, 0.5)+
  theme_apa()
```


```{r}
mainLoading2 <- 
resultsSVNP %>% 
  select(N, biasMainMean_2, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiasMainMean_2 = mean(biasMainMean_2)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasMainMean_2, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = NULL,
      y = NULL,
      title = " Main Loading 2")+
  ylim(0, 0.5)+
  theme_apa()
```

```{r}
mainLoading3 <- 
resultsSVNP %>% 
  select(N, biasMainMean_3, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiasMainMean_3 = mean(biasMainMean_3)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasMainMean_3, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = NULL,
      y = "Mean Absolute Bias",
      title = "Main Loading 3")+
  ylim(0, 0.5)+
  theme_apa()
```


```{r}
mainLoading4 <- 
resultsSVNP %>% 
  select(N, biasMainMean_4, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiasMainMean_4 = mean(biasMainMean_4)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasMainMean_4, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = NULL,
       y = NULL,
      title = "Main Loading 4")+
  ylim(0, 0.5)+
  theme_apa()
```

```{r}
mainLoading5 <- 
resultsSVNP %>% 
  select(N, biasMainMean_5, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiasMainMean_5 = mean(biasMainMean_5)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasMainMean_5, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = "Size Cross Loading",
       y = "Mean Absolute Bias",
      title = " Main Loading 5")+
    ylim(0, 0.5)+
  theme_apa()
```

```{r}
mainLoading6 <- 
resultsSVNP %>% 
  select(N, biasMainMean_6, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiasMainMean_6 = mean(biasMainMean_6)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasMainMean_6, group = label, col = label))+
  geom_point()+
  geom_line()+
  labs(x = "Size Cross Loading",
      y = NULL,
      title = "Main Loading 6")+
  ylim(0, 0.5)+
  theme_apa()
```


```{r, fig.width= 15}
mainLoadings <- mainLoading1+mainLoading2 +  mainLoading3+mainLoading4 + mainLoading5 +mainLoading6 

mainLoadings + plot_layout(guides = "collect", ncol = 2) & theme(legend.position = "bottom", legend.title = element_blank())
```


```{r, , fig.height = 15}
png(file = "~/Downloads/mainLoadings.png", width=400, height=600)
mainLoadings + plot_layout(guides = "collect", ncol = 2) & theme(legend.position = "bottom", legend.title = element_blank())
dev.off()
```

### Residual Variances



```{r}
theta1 <- 
resultsSVNP %>% 
  select(N, biasThetaMean_1, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiastheta1 = mean(biasThetaMean_1)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiastheta1, group = label, col = label))+
  geom_point()+
  geom_line()+
  labs(x = "Size Cross Loading",
      y = NULL,
      title = "Theta 1")+
  ylim(0, 0.5)+
  theme_apa()
theta1
```

```{r}
theta2 <- 
resultsSVNP %>% 
  select(N, biasThetaMean_2, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiastheta2 = mean(biasThetaMean_2)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiastheta2, group = label, col = label))+
  geom_point()+
  geom_line()+
  labs(x = "Size Cross Loading",
      y = NULL,
      title = "Theta 2")+
  ylim(0, 0.5)+
  theme_apa()
theta2
```

```{r}
theta3 <- 
resultsSVNP %>% 
  select(N, biasThetaMean_3, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiastheta3 = mean(biasThetaMean_3)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiastheta3, group = label, col = label))+
  geom_point()+
  geom_line()+
  labs(x = "Size Cross Loading",
      y = NULL,
      title = "Theta 3")+
  ylim(0, 0.5)+
  theme_apa()
theta3
```

```{r}
theta4 <- 
resultsSVNP %>% 
  select(N, biasThetaMean_4, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiastheta4 = mean(biasThetaMean_4)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiastheta4, group = label, col = label))+
  geom_point()+
  geom_line()+
  labs(x = "Size Cross Loading",
      y = NULL,
      title = "Theta 4")+
  ylim(0, 0.5)+
  theme_apa()
theta4
```

```{r}
theta5 <- 
resultsSVNP %>% 
  select(N, biasThetaMean_5, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiastheta5 = mean(biasThetaMean_5)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiastheta5, group = label, col = label))+
  geom_point()+
  geom_line()+
  labs(x = "Size Cross Loading",
      y = NULL,
      title = "Theta 5")+
  ylim(0, 0.5)+
  theme_apa()
theta5
```


```{r}
theta6 <- 
resultsSVNP %>% 
  select(N, biasThetaMean_6, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiastheta6 = mean(biasThetaMean_6)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiastheta6, group = label, col = label))+
  geom_point()+
  geom_line()+
  labs(x = "Size Cross Loading",
      y = NULL,
      title = "Theta 6")+
  ylim(0, 0.5)+
  theme_apa()
theta6
```

## ALL AT ONCE

```{r}
crossLoadingsLowBias <- 
resultsSVNP %>% 
  select(N, biasCrossMean_2, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
    cross, label) %>% 
  summarise(meanBiasCrossMean_2 = mean(biasCrossMean_2)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasCrossMean_2, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = NULL, 
       y = "Mean Absolute Bias",
      title = "Cross-Loading 2-5")+
  ylim(0, 0.5)+
  theme_apa()
```


```{r}
crossLoadingHighBias <- 
resultsSVNP %>% 
  select(N, biasCrossMean_1, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
    cross, label) %>% 
  summarise(meanBiasCrossMean_1 = mean(biasCrossMean_1)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasCrossMean_1, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(
        x = NULL,
       y = NULL,
      title = "Cross-Loading 1 & 6")+
  ylim(0, 0.5)+
  theme_apa()
```


```{r}
mainLoadingsLowBias <- 
resultsSVNP %>% 
  select(N, biasMainMean_1, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiasMainMean_1 = mean(biasMainMean_1)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasMainMean_1, group = label, col = label))+
  geom_point()+
  geom_line()+
  labs(x = NULL,
      y = "Mean Absolute Bias",
      title = "Main Loading 1, 2, 5 & 6")+
  ylim(0, 0.5)+
  theme_apa()
```

```{r}
mainLoadingsHighBias <- 
resultsSVNP %>% 
  select(N, biasMainMean_3, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiasMainMean_3 = mean(biasMainMean_3)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasMainMean_3, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = NULL,
       y = NULL,
      title = "Main Loading 3 & 4")+
  ylim(0, 0.5)+
  theme_apa()
```

```{r}
factCorr <- 
resultsSVNP %>% 
  select(N, biasFactCorrMean, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiasFactCorrMean = mean(biasFactCorrMean)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiasFactCorrMean, group = label, col = label))+
  geom_point()+
  geom_line()+
  #facet_wrap(~N)+
  labs(x = "Size Cross Loading",
       y = "Mean Absolute Bias",
      title = "Factor Correlation")+
  ylim(0, 0.5)+
  theme_apa()
```

```{r}
thetas <- 
resultsSVNP %>% 
  select(N, biasThetaMean_1, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiastheta1 = mean(biasThetaMean_1)) %>% 
  ggplot(aes(x = as.factor(cross), y = meanBiastheta1, group = label, col = label))+
  geom_point()+
  geom_line()+
  labs(x = "Size Cross Loading",
       y = NULL,
       title = "Theta 1-6")+
  ylim(0, 0.5)+
  theme_apa()
```

```{r, fig.height = 15}
allAtOnce <- crossLoadingsLowBias + crossLoadingHighBias + mainLoadingsLowBias + mainLoadingsHighBias + factCorr + thetas
allAtOnce + plot_layout(guides = "collect", ncol = 2) & theme(legend.position = "bottom", legend.title = element_blank())
```

```{r, fig.height = 15}
png(file = "~/1vs2StepBayesianRegSEM/Rmd/figures/allPars.png", width=400, height=550)
allAtOnce + plot_layout(guides = "collect", ncol = 2) & theme(legend.position = "bottom", legend.title = element_blank())
dev.off()
```



## Making sense of the plots

### zero cross-loadings

```{r}
resultsSVNP %>% 
  select(N, biasCrossMean_2, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
    cross, label) %>% 
  summarise(meanBiasCrossMean_2 = mean(biasCrossMean_2))
```

```{r}
resultsSVNP %>% 
  select(N, crossEstMean_2, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
    cross, label) %>% 
  summarise(meanCrossEstMean_2 = mean(crossEstMean_2))
```


### non-zero cross-loadings

```{r}
resultsSVNP %>% 
  select(N, biasCrossMean_1, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
    cross, label) %>% 
  summarise(meanBiasCrossMean_1 = mean(biasCrossMean_1)) 
```

```{r}
resultsSVNP %>% 
  select(N, crossEstMean_1, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
    cross, label) %>% 
  summarise(meanCrossEstMean_1 = mean(crossEstMean_1))
```

### High-Bias Main Loadings

```{r}
resultsSVNP %>% 
  select(N, biasMainMean_3, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiasMainMean_3 = mean(biasMainMean_3))
```

```{r}
resultsSVNP %>% 
  select(N, mainEstMean_3, cross, sigmaSqu) %>%
  mutate(label = as.factor(paste0("\u03c3\u00B2 = ", sigmaSqu))) %>% 
  group_by(#N, 
           cross, label) %>% 
  summarise(meanBiasMainMean_3 = mean(biasMainMean_3))
```

